---
title: "Assignment-b4"
author: "April Hwang"
date: "2023-11-28"
output: html_document
---

# Setup
```{r}
library(janeaustenr)
library(stringr)
library(tidytext)
library(stopwords)
library(ggplot2)
library(tidytext)
suppressPackageStartupMessages(library(devtools))
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(dplyr))
```

<br>

# Exercise 1 (37.5 points)
For this exercise, I will take the book _Emma_ from the `janeaustenr` package and make a plot of the most common words in the book. I will be removing stop words using the `stopwords` package.

Link to the `stopwords` package is available here: https://github.com/quanteda/stopwords

## One-row-per-line format

```{r}
#one-row-per-line format, annotate line numbers and chapters
row_per_line <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

row_per_line
```


## One-token-per-row format 

```{r}
#use unnest_tokens()
token_per_row <- row_per_line %>%
  unnest_tokens(word, text)

token_per_row
```


## Remove stop words
```{r}
stop_words_removed <- token_per_row %>%
  anti_join(get_stopwords())

stop_words_removed
```

## Select _Emma_
```{r}
em <- stop_words_removed %>%
  filter(book == 'Emma')

em
```


## Count words
```{r}
common_words <- em %>%
  count(word, sort = TRUE) 

common_words
```


## Plot top ten most common words from _Emma_
```{r}
plot_em <- common_words %>%
  slice_max(n, n = 10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
    geom_point()

plot_em
```

<br>

# Exercise 2 (37.5 points)

For this exercise, I will make a function called `bunnylatin` that converts words to my own version of Pig Latin.

For the rearrangement component, I will move the last two letters from the end to the beginning. For the addition component, I will repeat the last letter to the end of the word following the rearrangement. For example, if the word is 'apple', it will first rearrange the word by moving the last two letters to the beginning ('leapp'), then repeat the last letter at the end of the word ('leappp')

The input of must be a string or a vector. Each string length must be equal to or greater than three. 


```{r}
bunnylatin <- function(x) {
  stopifnot('Too short! String length must be equal to or greater than three.' =
              stringr::str_length(x) >2)
  last_two <- stringr::str_sub(x, -2, -1)
  first <- stringr::str_sub(x, 1, -3)
  last_letter <- stringr::str_sub(first, -1)
  stringr::str_c(last_two, first, last_letter)
}
```

