---
title: "Assignment-b4"
author: "April Hwang"
date: "2023-11-28"
output: html_document
---

# Setup
```{r}
library(janeaustenr)
library(stringr)
library(tidytext)
library(stopwords)
library(ggplot2)
suppressPackageStartupMessages(library(devtools))
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(dplyr))
```

<br>

# Exercise 1 (37.5 points)
For this exercise, I will take the book _Emma_ from the `janeaustenr` package and make a plot of the most common words in the book. I will be removing stop words using the `stopwords` package.

Link to the `stopwords` package is available here: https://github.com/quanteda/stopwords

## One-row-per-line format
```{r}
original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(line = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books
```


## One-token-per-row format
```{r}
tidy_books <- original_books %>%
  unnest_tokens(output = word, input = text)

tidy_books
```


## Remove stop words
```{r}
cleaned_books <- tidy_books %>%
  anti_join(get_stopwords())

cleaned_books
```

## Select _Emma_
```{r}
em <- cleaned_books %>%
  filter(book == 'Emma')

em
```


## Count words
```{r}
common_words <- em %>%
  count(word, sort = TRUE) 

common_words
```


## Plot top ten most common words from _Emma_

```{r}
plot <- common_words %>%
  slice_max(n, n = 10) %>%
  ggplot(aes(x = word, y = n)) +
    geom_point()

plot
```

<br>

# Exercise 2 (37.5 points)

For this exercise, I will make a function called `bunny_latin` that converts words to my own version of Pig Latin.

For the rearrangement component, I will move the last two letters from the end to the beginning. For the addition component, I will add the last letter to the end of the word following the rearrangement. For example, if the word is 'apple', it will first rearrange the word by moving the last two letters to the beginning ('leapp'), then add the last letter to the end of the word ('leappp')


The specific input and output that you decide upon is up to you. Don’t forget to implement good function-making hygiene: we’ll be looking for (unrendered) roxygen2-style documentation (being sure to describe your Pig Latin conversion), examples of applying the function, 3 non-redundant tests, appropriate use of arguments, and appropriate amount of checking for proper input.

```{r}
#take last two letters of word
#last_two <- str_sub(words, -2, -1)

#word minus last two letters
#first <- str_sub(words, 1, -3)

#last letter of word
#last_letter <- str_sub(first, -1)

#bunny latin
#bunny_latin <- str_c(last_two, first, last_letter)
```



```{r}
bunnylatin <- function(x) {
  last_two <- str_sub(x, -2, -1) 
  first <- str_sub(x, 1, -3)
  last_letter <- str_sub(first, -1) 
  str_c(last_two, first, last_letter)
    
}
```

