---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bunnylatin

<!-- badges: start -->
<!-- badges: end -->

The purpose of `bunnylatin` is to make a variation of Pig Latin. It allows users to conveniently convert a string or a vector into Bunny Latin. 

## Installation

You can install the development version of bunnylatin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/bunnylatin")
```

## Usage

You can use `bunnylatin` to easily manipulate a string or a vector according to the Bunny Latin rules. It will move the last two letters of the word to the front, then repeat the last letter of the newly modified word once at the end.

## Example

Here are some basic examples of how to use `bunnylatin`:

```{r example}
library(bunnylatin)

#'apple' will return 'leappp'
bunnylatin('apple')

#'12345' will return '451233'
bunnylatin('12345')

#c('summer', 'sunshine', 'puppy') will return c('ersummm', 'nesunshii', 'pypupp')
bunnylatin(c('summer', 'sunshine', 'puppy'))
```
